### 2011-09-24 doc/theses/vitasek/chapter-1-definitions.tex
Thesis: in progress.

\begin{figure}
  \caption{Example XML Tree}
  \label{image-definitions-example-xml-tree}
  \centering
    \includegraphics[width=\textwidth]{images/definitions/xml-tree}
\end{figure}

@@

\section{ID, IDREF, IDREFS Attributes}

@@

\begin{define}[Attribute mapping]
	For $x \in \Sigma^E$ and $y \in \Sigma^A$ we define the attribute mapping of y over x, denoted $M_{x}^{y}$, the $I \times I$ % TODO fix the capital I
	relation defined by
	\[M_{x}^{y} = \{ (z,w): label(z) = x, label(w) = y, parent(w) = z \}\]
\end{define}

@@

TODO more from the article?

\paragraph{Example}
The XML tree from Figure \ref{image-definitions-example-xml-tree} has the following non-empty AMs: $M_{y}^{a} = \{(2,6), (3,8)\}$, $M_{y}^{b} = \{(2,7)\}$, $M_{y}^{c} = \{(3,9)\}$ and $M_{z}^{a} = \{(5,10)\}$.

@@

@@

@@

@@

>>>>

\begin{figure}
  \caption{Example XML Tree}
  \label{image-definitions-example-xml-tree}
  \centering
    \subfigure[XML tree]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree}}
    \subfigure[Attribute mappings]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree-ams}}
\end{figure}

@@

\section{ID, IDREF, IDREFS Attributes}
\label{section-definitions-id-attributes}

@@

\begin{define}[Attribute mapping]
	For $x \in \Sigma^E$ and $y \in \Sigma^A$ we define the \textit{attribute mapping} of y over x, denoted $M_{x}^{y}$, the $I \times I$ % TODO fix the capital I
	relation defined by
	\[M_{x}^{y} = \{ (z,w): label(z) = x, label(w) = y, parent(w) = z \}\]
\end{define}

@@

We can use projection to retrieve all the unique \textit{ids} of either elements or attributes from the relation, with notation $\pi_E(M_{x}^{y})$ and $\pi_A(M_{x}^{y})$.

\begin{define}[Type of the attribute mapping]
	Attribute mapping $M_{x}^{y}$ is of the \textit{type} $\tau(M_{x}^{y}) = x$.
\end{define}

\paragraph{Example}
The XML tree from Figure \ref{image-definitions-example-xml-tree} has the following non-empty AMs drawn in bold lines: $M_{y}^{a} = \{(2,6), (3,8)\}$, $M_{y}^{b} = \{(2,7)\}$, $M_{y}^{c} = \{(3,9)\}$ and $M_{z}^{a} = \{(5,10)\}$.

Following example equations hold.
\begin{eqnarray*}
\pi_E(M_{y}^{a}) & = & \{2, 3\} \\
\pi_A(M_{z}^{a}) & = & \{10\} \\
\tau(M_{y}^{c}) & = & y
\end{eqnarray*}

\begin{define}[Image of the attribute mapping]
	\textit{Image} $\iota$ of the attribute mapping $M_{x}^{y}$ is defined as $\iota(M_{x}^{y}) = \{z: z = value(w), w \in \pi_A(M_{x}^{y})\}$
\end{define}

So the image of an AM is a set of all the values of all the attribute nodes contained in the mapping.

\paragraph{Example}
Again referring to the XML tree from \ref{image-definitions-example-xml-tree}, we get the following AM images.
\begin{eqnarray*}
\iota(M_{y}^{a}) & = & \{1, 3\} \\
\iota(M_{y}^{b}) & = & \{2\} \\
\iota(M_{y}^{c}) & = & \{4\} \\
\iota(M_{z}^{a}) & = & \{1\} \\
\end{eqnarray*}

@@

Based on the requirements for an ID attribute from Section \ref{section-definitions-id-attributes} we will define ID set with the help of the following definition.

\begin{define}[Candidate attribute mapping]
An attribute mapping $m$ is a \textit{candidate attribute mapping} if it is an injective function, that is,
\[|m| = |\pi_E(m)| = |\pi_A(m)| = |\iota(m)|\]
\end{define}

\paragraph{Example}
In our example all the attribute mappings are candidate AMs.

Now we can proceed to define an ID set.

\begin{define}[ID set]
A set of candidate attribute mappings $I = \{m_1, \ldots m_n\}$ is an ID set iff
\[\bigcap_{m_i \in I} \tau(m_i) = \emptyset \wedge \bigcap_{m_i \in I} \iota(m_i) = \emptyset\]
\end{define}

That is, an ID set has images without repeating values and all the types are unique (an element cannot have more than one ID attribute).

\paragraph{Example}
Returning to our example, the following are all the possible ID sets: $\{ M_{y}^{a} \}, \{ M_{y}^{b} \}, \{ M_{y}^{b}, M_{z}^{a} \}, \{ M_{y}^{c} \}, \{ M_{y}^{c}, M_{z}^{a} \}$. Note that once we select an AM of type $y$ we can never add any other with the same type. Note also that $\{ M_{y}^{c}, M_{z}^{a} \}$ is not an ID set, because $\iota(M_{y}^{c}) \cap \iota(M_{z}^{a}) \neq \emptyset$.

\subsection{IDREF and IDREFS Attributes}

@@

TODO this is from FIDAX again

$M = \{m_1, \dots m_i\}$ is the set of all non-empty AMs in the document.

@@

\begin{define}[Support]
\textit{Support} of an attribute mapping $m$ is defined as follows.
\[\phi(m) = \frac{|m|}{\sum_{p \in M}|p|}\]
\end{define}

TODO example

@@

\begin{define}[Coverage]
\textit{Coverage} of an attribute mapping $m$ is defined as follows.
\[\chi(m) = \left( \sum_{p \in M, p \neq m} |\iota(m) \cap \iota(p)| \right) / \sum_{p \in M} |\iota(p)|\]
\end{define}

TODO example

### 2011-09-24 doc/theses/vitasek/chapter-5-future.tex
Thesis: in progress.

It is possible (and easy) to add more construction and improvement heuristics, as well as more metaheuristics in which the existing IHs are chained. A starting point is in Section TODO link appendix - how to write...\\

As it was mentioned in TODO link, the combination of \heu{Crossover}, \heu{Mutation} and \heu{RemoveWorst} can be seen as a sort of genetic programming. However some modifications would still be necessary to make it a real instance of genetic algorithm metaheuristic.

@@

The approach used in this work was strictly single-threaded, however there are in principle no limitations to extending this to a parallel, multi-threaded environment. For example, creating a pool of initial solutions in \heu{Glpk} construction heuristic can be improved by running several instances of GLPK solver in parallel - as GLPK on its own uses only a single thread to perform the computation.\\

>>>>

It is possible (and easy) to add more construction and improvement heuristics, as well as more metaheuristics in which the existing IHs are chained. A starting point is in Section \ref{section-appendix-iss-howto}.\\

As it was mentioned in Section \ref{section-mip-ihs}, the combination of \heu{Crossover}, \heu{Mutation} and \heu{RemoveWorst} can be seen as a sort of genetic programming. However some modifications would still be necessary to make it a real instance of genetic algorithm metaheuristic.

@@

The approach used in this work was strictly single-threaded, however there are in principle no limitations to extending this to a parallel, multi-threaded environment. For example, creating a pool of initial solutions in \heu{Glpk} construction heuristic can be improved by running several instances of GLPK solver in parallel - as GLPK on its own uses only a single thread.\\
